Identification of DC Pixels using Boosted Decision Trees

### 2016-05-10 report/draft1.tex
Backup 10/5/16

\subsection{CORSIKA}
A full simulation of Cosmic Ray air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia. The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{2.7}$. Four random seed numbers were passed to the program, generated using the overall job number and the run number corresponding to the parallel computing task index. Thus, for each set of simulations, 4 unique random number seeds were used. An altitude of 1800m was assumed, again corresponding to the HESS site. The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$. The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center. The length of each cross arm was $85m$. The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.

In order to identify the DC pixel, each simulation run with an energy cut of 10 PeV on all muons and electrons. The consequence of this was to ensure that only the Cherenkov Light from the primary particle, as well as its fragments, was simulated. A second identical simulation was run with the same random seeds but without the energy cut on muons and electrons, giving a complete air shower including the DC light.

\subsection{Sim\textunderscore telarray}
Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected hardware response to the air shower can be simulated. Again, the built-in response of the HESS telescope was selected for simulation. The program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses. The resultant images can be considered representative of true camera images to a good approximation. For the second, full, simulation, the night sky background was also simulated.

A script was written to extract the location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated Intensity. THe HESS telescope has both a low gain Channel 0 and a high gain Channel 1. In the case of many iron core events, Channel 0 will reach its maximum value and become saturated. Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels, so was not used in this analysis. Instead, only the Channel 1 ADC was extracted by the script, and will be referred to throughout this analysis as $Count$. For use in later calculation, the pedestal and calibration of each pixel was recorded.

In addition to the $Count$ of each pixel, the Sim\textunderscore telarray derives various Hillas whole-image parameters, which the script also extracted. These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated. Further the reconstructed shower direction and the shower center of gravity were calculated as positions in azimuth and zenith. Additionally the calculated energy and distance to core $r_{core}$ were recorded.

An entry was constructed for every pixel, containing its count and position. The variables $ \Delta_{C.o.G}$, $\Delta_{Direction}$ and $\Delta_{Line}$ were defined as the distance from the pixel to the shower center of gravity, shower direction, and the line joining those two points. Furthermore, the nearest neigbouring pixel IDs were calculated for every pixel position, enabling the count in each neighbouring pixel to be found. From this, two further pixel variables were defined. The largest neighbouring count $Count_{N.N.max}$ was found, and the ratio $ Q_{DC} = \frac{Count}{Count_{N.N.max}} $ was derived. In addition the Nearest Neighbour Mean Count was recorded. These variables were recorded in every pixel entry, and together the pixel entries formed a complete dataset for each camera image.

@@

From the subset of pixels satisfying these conditions, the remaining pixel with the largest $Q_{DC}$ was selected as the DC pixel. The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut. Out of 400 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Count_{DC} > 5500$ in the hadron-only image. SOMETHING! Of this subset of 'DC events', 17\% events passed all of the required cuts. The $Q_{DC}$ was found to be 100\% accurate in identifying the DC pixel in those passing events, as shown in \ref{fig:cutdistribution}.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{cutdistribution}
\caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000. Events below this are unlikely to be identified correctly because the DEC light is too faint. In the top right- the distribution of the dataset is shown, once all the non-$Q_{DC}$ cuts have been applied. In the bottom left, the BDT score distribution is shown before any cuts. On the bottom right, we see the same distribution after both signal and BDT score cuts are applied. All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.}
\label{fig:cutdistribution}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{DCcounterror}
\caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left. In the top right the same is shown for events which were rejected. The true DC signals for events which passed the cuts is plotted against the reconstructed signals in the lower left, and for rejected events in the lower right. As in \ref{fig:cutdistribution}, in all plots a green event is one in which the DC pixel has been correctly identified, while a red event is one that has been incorrectly identified.}
\label{fig:dcdiff}
\end{center}
\end{figure}

>>>>

\subsection{CORSIKA}
A full simulation of Cosmic Ray air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia. The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{-2.7}$. For each set of simulated event, 4 unique random number seeds were used to generate the shower. An altitude of 1800m was assumed, again corresponding to the HESS site. The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$. The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center. The length of each cross arm was $85m$. The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.

In order to identify the DC pixel, a \textquoteleft DC Simulation' was initially run with an energy cut of 10 PeV on all muons and electrons. The consequence of this was to ensure that only the Cherenkov Light from the primary particle, as well as its fragments, was simulated. A second identical \textquoteleft Full Simulation' was run including the same random seeds, but without the energy cut on muons and electrons. This gave a complete air shower including the DC light, representative of those imaged in telescope arrays. Comparisons of the Full and DC simulations enabled us to identify background light in the Full shower.

\subsection{Sim\textunderscore telarray}
Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected hardware response to an air shower can be simulated. Again, the built-in response of the HESS telescope was selected for simulation. The program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses. Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered representative of true camera images. For the Full Simulation, the night sky background was also simulated by sim\textunderscore telarray.

The HESS telescope has both a high gain Channel 0 and a low gain Channel 1. The location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated value of SOMETHING? in each value was extracted. The pedestal and gain for each channel was also recorded, and from this, Intensity can be found.

\[ Intensity = (Count - Pedestal)\times Gain \]

In the case of many iron core events, Channel 0 will reach its maximum value and become saturated. Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels, so was not used in this analysis. Instead, only the Channel 1 was used in later analysis. Thus the Channel 1 Intensity will simply be referred to throughout this analysis as $Intensity$.

In addition to the $Intensity$ of each pixel, the Sim\textunderscore telarray derives various Hillas whole-image parameters, which the script also extracted. These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated. Further the reconstructed shower direction and the shower center of gravity were calculated as positions in azimuth and zenith. Additionally the calculated energy and distance to core $r_{core}$ were recorded.

An entry was constructed for every pixel, containing its count and position. The variables $ \Delta_{C.o.G}$, $\Delta_{Direction}$ and $\Delta_{Line}$ were defined as the distance from the pixel to the shower center of gravity, shower direction, and the line joining those two points. Furthermore, the nearest neigbouring pixel IDs were calculated for every pixel position, enabling the count in each neighbouring pixel to be found. From this, two further pixel variables were defined. The largest neighbouring intensity $Intensity_{N.N.max}$ was found, and the ratio $ Q_{DC} = \frac{Intensity}{Intensity_{N.N.max}} $ was derived. In addition the Nearest Neighbour Mean Count was recorded. These variables were recorded in every pixel entry, and together the pixel entries formed a complete dataset for each camera image.

@@

From the subset of pixels satisfying these conditions, the remaining pixel with the largest $Q_{DC}$ was selected as the DC pixel. The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut. Out of 400 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Intensity_{DC} > 150$ in the hadron-only image. SOMETHING! Of this subset of 'DC events', 17\% events passed all of the required cuts. The $Q_{DC}$ was found to be 100\% accurate in identifying the DC pixel in those passing events, as shown in \ref{fig:cutdistribution}.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{cutdistributionhess1}
\caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000. Events below this are unlikely to be identified correctly because the DEC light is too faint. In the top right- the distribution of the dataset is shown, once all the non-$Q_{DC}$ cuts have been applied. In the bottom left, the BDT score distribution is shown before any cuts. On the bottom right, we see the same distribution after both signal and BDT score cuts are applied. All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.}
\label{fig:cutdistribution}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{DCcounterrorhess1}
\caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left. In the top right the same is shown for events which were rejected. The true DC signals for events which passed the cuts is plotted against the reconstructed signals in the lower left, and for rejected events in the lower right. As in \ref{fig:cutdistribution}, in all plots a green event is one in which the DC pixel has been correctly identified, while a red event is one that has been incorrectly identified.}
\label{fig:dcdiff}
\end{center}
\end{figure}
